Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments

### 2013-09-12 article/article.tex
Add abstract to the article

\title{Automatic scaling of users' application deployed in a federation of cloud computing environments}

@@

\author{Dariusz Chrząścik          \and
        Radosław Morytko
}

@@

\institute{D. Chrząścik \at
  \email{dariusz@chrzascik.com}           %  \\
  \and
  R. Morytko \at
  \email{radoslaw@morytko.pl}
}

@@

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{cloud computing\and application scaling \and intercloud \and hybrid configuration}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Your text comes here. Separate text sections with
\section{Section title}
\label{sec:1}
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

% For one-column wide figures use
%\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:1}       % Give a unique label
%\end{figure}
%
% For two-column wide figures use
%\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:2}       % Give a unique label
%\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

>>>>

\title{Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments}

@@

\author{Dariusz Chrząścik          \and
        Radosław D. Morytko
}

@@

\institute{
  D. Chrząścik \\
  Chief Technology Officer at Software Mind SA \\
  Enthusiast of gorgeous cars and fast women \\
  Amateur poet, screenwriter and novelist\at
  \email{dariusz@chrzascik.com}           %  \\
  \and
  R.D. Morytko \\
  Software Developer and Board Member at Dropsport \\
  Devoted admirer of Gothic cathedrals \\
  Amateur guitar player and zumba dancer\at
  \email{radoslaw@morytko.pl}
}

@@

\begin{abstract}
In order to retain the lead among its competitors, a software company needs to create a distributed system which is spanned across different geographical locations, vulnerable to sudden variations in demand and has remarkable QoS requirements. Following current trends it chooses Cloud as a deployment platform. Unfortunately, existing cloud providers do not have tools and mechanisms that would enable dynamic load distribution among different data centers to meet aforementioned requirements.
In this article we want to outline the architecture of a self-adaptive platform which facilitates scalable provisioning users' applications and fulfills QoS needs under variable conditions. Our solution can be considered a multi-layered environment for users' services as it applies the notion of an autonomic system to its every layer on a which auto scaling can be executed -- application, container, service and cloud. To ensure meeting QoS requirements at the cloud level we use the recent concept of a utility-oriented federation of cloud environments (InterCloud).
We present and compare current cloud solutions with the emphasis on their scaling capabilities. Finally, we demonstrate our preliminary results of conducted evaluation studies on the CloudSim toolkit.

\keywords{cloud computing\and application scaling \and intercloud \and hybrid configuration}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Dizffko
\section{Section title}
\label{sec:1}
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

% For one-column wide figures use
%\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:1}       % Give a unique label
%\end{figure}
%
% For two-column wide figures use
%\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
%  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
%\caption{Please write your figure caption here}
%\label{fig:2}       % Give a unique label
%\end{figure*}
%
% For tables use
%\begin{table}
% table caption is above the table
%\caption{Please write your table caption here}
%\label{tab:1}       % Give a unique label
% For LaTeX tables use
%\begin{tabular}{lll}
%\hline\noalign{\smallskip}
%first & second & third  \\
%\noalign{\smallskip}\hline\noalign{\smallskip}
%number & number & number \\
%number & number & number \\
%\noalign{\smallskip}\hline
%\end{tabular}
%\end{table}
